Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
double cycle, double path

\centerline{
\begin{tikzpicture}[
	scale=2,
	thick,
	decoration={markings, mark=at position 0.5 with {\arrow{>}}},
	roundNode/.style={circle, fill=black, inner sep=2pt, outer sep=2pt}
	]
	\node[roundNode, label=left:{$s(\alpha)$}] (s) at (-1,0) {};
	\node[roundNode, label=right:{$t(\alpha)$}] (t) at (1,0) {};
	\node[roundNode, fill=green, label=above:{$\green v(\alpha)$}] (v) at (0,1) {};
	\node[roundNode, fill=red, label=below:{$\red v\dual(\alpha)$}] (vd) at (0,-1) {};
	\draw[color=black, postaction={decorate}] (s) -> (t) node[midway, above] {$\alpha$};
	\pic [draw, angle radius=.7cm] {angle = s--t--vd};
	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
	\draw[color=green, postaction={decorate}] (v) -> (s) node[midway, above left] {$\green \Enrs{\alpha}$};
	\draw[color=green, postaction={decorate}] (v) -> (t) node[midway, above right] {$\green \Enrt{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (s) node[midway, below left] {$\red \Ers{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (t) node[midway, below right] {$\red \Ert{\alpha}$};
\end{tikzpicture}
}

@@

\begin{example}
Consider the following family of locally gentle quivers:
\vincent{TODO}
\end{example}

>>>>

\centerline{
\begin{tikzpicture}[
	scale=1.5,
	thick,
	decoration={markings, mark=at position 0.5 with {\arrow{>}}},
	roundNode/.style={circle, fill=black, inner sep=2pt, outer sep=1.5pt}
	]
	\node[roundNode, label={[label distance=-3pt]left:{$s(\alpha)$}}] (s) at (-1,0) {};
	\node[roundNode, label={[label distance=-3pt]right:{$t(\alpha)$}}] (t) at (1,0) {};
	\node[roundNode, fill=green, label={[label distance=-3pt]above:{$\green v(\alpha)$}}] (v) at (0,1) {};
	\node[roundNode, fill=red, label={[label distance=-3pt]below:{$\red v\dual(\alpha)$}}] (vd) at (0,-1) {};
	\draw[color=black, postaction={decorate}] (s) -> (t) node[midway, above] {$\alpha$};
	\pic [draw, angle radius=.7cm] {angle = s--t--vd};
	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
	\draw[color=green, postaction={decorate}] (v) -> (s) node[midway, above left, outer sep=-3pt] {$\green \Enrs{\alpha}$};
	\draw[color=green, postaction={decorate}] (v) -> (t) node[midway, above right, outer sep=-3pt] {$\green \Enrt{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (s) node[midway, below left, outer sep=-3pt] {$\red \Ers{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (t) node[midway, below right, outer sep=-3pt] {$\red \Ert{\alpha}$};
\end{tikzpicture}
}

@@

\begin{example}[Double cycle]
\label{exm:doubleCycle}
Consider the following family of locally gentle quivers:
\vincent{TODO double cycle}
\end{example}

\begin{example}[Double path]
\label{exm:doublePath}
Consider the following family of locally gentle quivers:
\vincent{TODO double path}
\end{example}
